Sensitivity Analysis

### 2024-03-19 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Experiments.tex
14.03
19.03

	In order to solve the optimization problem presented by Equation \ref{EQ: Optimization_formulation_MLE}, it is necessary to have knowledge of the dataset ${\color{black}Y}(t)$, which was obtained by extracting oil from chamomile flowers. The experiments were performed by \citet{Povh2001}. To prepare the flowers for extraction, they were first pre-treated using a knife mill (TECNAL, model TE 340) to reduce their particle size. The mean
	particle diameter was determined by the Sauter equation and is equal to $0.3\times 10^{-3}$m. The actual density of the chamomile particles was measured through helium pycnometry at the Institute of Chemistry IQ/Unicamp's Analytical Facilities. The bulk density of the bed was computed based on the feed's mass and the extractor's volume. The total porosity of the bed, including the particles, was determined using the following calculation: $\epsilon=1-\frac{d_a}{d_r} = 1-\frac{370}{1364} = 0.73$.

@@

	The experiments were conducted using an extractor with diameter of $3.96\times 10^{-2}$ m and length $16.55\times 10^{-2}$ m. Twelve experiments were performed under different but constant in time operating conditions: $30-40^\circ C$, $100 - 200$ bar, and $1.33-6.67 \times 10^{-5}$ kg/s. The amount of solid material used for extraction was $75\times 10^{-3}$ kg, which was sufficient to fill the whole vessel. Samples were collected every 30 min for the first 3 h and every hour afterwards up to 10 h.

>>>>

	In order to solve the optimization problem presented by Equation \ref{EQ: Optimization_formulation_MLE}, it is necessary to have knowledge of the dataset ${\color{black}Y}(t)$, which was obtained by extracting oil from chamomile flowers. The experiments were performed by \citet{Povh2001} and \citet{Rahimi2011}. To prepare the flowers for extraction, they were first pre-treated using a knife mill (TECNAL, model TE 340) to reduce their particle size. The Sauter equation determined the mean particle diameter and is equal to $0.3\times 10^{-3}$m. The actual density of the chamomile particles was measured through helium pycnometry at the Institute of Chemistry IQ/Unicamp's Analytical Facilities. The bulk density of the bed was computed based on the feed's mass and the extractor's volume. The total porosity of the bed, including the particles, was determined using the following calculation: $\epsilon=1-\frac{d_a}{d_r} = 1-\frac{370}{1364} = 0.73$.

@@

	The experiments were conducted using an extractor with a diameter of $3.96\times 10^{-2}$ m and a length $16.55\times 10^{-2}$ m. Twelve experiments were performed under different but constant in time operating conditions: $30-40^\circ C$, $100 - 200$ bar, and $1.33-6.67 \times 10^{-5}$ kg/s. The amount of solid material used for extraction was $75\times 10^{-3}$ kg, which was sufficient to fill the whole vessel. Samples were collected every 30 min for the first 3 h and every hour afterwards up to 10 h.

### 2024-03-19 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Model.tex
19.03

	Assuming that the mass flow rate is constant in time, the temporal derivative becomes zero, and the spatial derivative can be integrated along ${\color{black}z}$ as

	{\footnotesize
		\begin{equation}
			\int \frac{\partial ({\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) v {\color{black}A \phi}(z) )}{\partial {\color{black}z}} dz = 0 \rightarrow {\color{black}F}={\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) v {\color{black}A\phi}(z)
		\end{equation}
	}

	Here, ${\color{black}F}$ is a constant obtained from the integration and is understood as the mass flux per unit area, which is assumed to be constant along ${\color{black}z}$. To simplify the dynamics of the system, it is assumed that ${\color{black}F}={\color{black}F}(t)$ is a control variable and affects the whole system instantaneously. This assumption allows for finding the velocity profile that satisfies mass continuity based on ${\color{black}F}(t)$, ${\color{black}\phi}(z)$, and ${\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t))$.

@@

	The fluid density ${\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t))$ can be obtained from an equation of state if temperature and the thermodynamic pressure (assumed ${\color{black}P}(t)$ to be constant along ${\color{black}z}$ due to the low-Mach number condition) are known. The variation in density may be caused by the fluid accumulation in the system (equivalent to pressure change), which occurs instantaneously along ${\color{black}z}$ or by a temperature change.

@@

	The comprehensive derivation of the mass balance equation for the fluid phase is detailed in Appendix \ref{CH: Gouverning equations}. This equation accounts for the movement of the pseudo-homogeneous fluid phase (Equation \ref{Model_fluid}), which is constrained to the axial direction due to the quasi-one-dimensional approach that considers changes in the void fraction. It is also predicated on the assumption that the thermodynamic pressure remains constant throughout the device, as illustrated by Equation \ref{EQ: Pressure_Velocity}. The analysis further simplifies the flow dynamics by disregarding the boundary layer near the extractor's inner wall, leading to a uniform velocity profile across any cross-section perpendicular to the axial direction. Given that the solute concentration in the solvent is negligible, the fluid phase is described as pseudo-homogeneous, with properties identical to the solvent itself. The mass balance equation thus encompasses convection, diffusion, and kinetic terms to accurately represent the fluid phase's behaviour.

@@

		The efficiency of the process (the yield) is calculated according to Equation \ref{Model_measurment_1} as presented by \citet{Sovova1994a}. The measurement equation evaluate the mass of solute at the outlet of the extraction unit and sums it. The integral form of the measurement equation (\ref{Model_measurment_1}) can be transformed into the differential form (\ref{Model_measurment_2}) and augmented with the process model.

@@

		\subsubsection{Initial and boundary conditions} 
		It is assumed that the solvent is free of solute at the entrance of the extractor and that all the solid particles have the same initial solute content ${\color{black}c_{s0}}$. As the residence time is much shorter than the sampling time, the initial state estimate for the concentration of the solute in the fluid phase would be not reliable. Considering that it is assumed that the $c_{f0}=0$. Moreover, it is considered that the extractor is isothermal %and described by ${\color{black}h_0}$. 
		Therefore, the initial and boundary conditions employed in the simulation are:

@@

			{\footnotesize
				\begin{align*}
					&{\color{black}c_f}(t = 0, z) = 0 & {\color{black}c_s}(t = 0, z) = {\color{black}c_{s0}} &{c_f}(t, z=0) = 0 \\
					&\frac{\partial c_f(t,z=0,L)}{\partial x} = 0 & c_s(t, z=0,L) = {\color{black}c_{s0}} &y(0) = 0
			\end{align*} }

@@

		As presented in Appendix \ref{CH: Gouverning equations}, all the governing can be written in the integral form using the Divergence Theorem. The integral equation states that the change rate of the integral of any quantity over an arbitrary control volume is given by the flux through the boundary of the control volume, with being the outer surface normal through the boundary. That quantity is neither produced nor consumed inside the control volume and is conserved. For a derivative to be conservative, it must form a telescoping series. In other words, after the addition of all terms coming from the discretization over a grid, only the boundary terms should remain, and the artificial interior points should cancel out. To ensure mass conservation, discretization is applied to the conservative form of the process model.

>>>>

	Assuming that the mass flow rate is constant in time, the temporal derivative becomes the mass flux F, and the spatial derivative can be integrated along ${\color{black}z}$ as

	{\footnotesize
		\begin{equation}
			\int \frac{\partial ({\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) v {\color{black}A \phi}(z) )}{\partial {\color{black}z}} dz = F \rightarrow {\color{black}F}={\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) v {\color{black}A\phi}(z)
		\end{equation}
	}

	To simplify the dynamics of the system, it is assumed that ${\color{black}F}={\color{black}F}(t)$ is a control variable and affects the whole system instantaneously. This assumption allows for finding the velocity profile that satisfies mass continuity based on ${\color{black}F}(t)$, ${\color{black}\phi}(z)$, and ${\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t))$.

@@

	The fluid density ${\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t))$ can be obtained from an equation of state (Appendix \ref{CH: EOS}) if temperature and the thermodynamic pressure (assumed ${\color{black}P}(t)$ to be constant along ${\color{black}z}$ due to the low-Mach number condition) are known. The variation in density may be caused by the fluid accumulation in the system (equivalent to pressure change), which occurs instantaneously along ${\color{black}z}$ or by a temperature change.

@@

	The comprehensive derivation of the mass balance equation for the fluid phase is detailed in Appendix \ref{CH: Gouverning equations}. This equation accounts for the movement of the pseudo-homogeneous fluid phase (Equation \ref{Model_fluid}), which is constrained to the axial direction due to the quasi-one-dimensional approach that considers changes in the void fraction. It is also predicated on the assumption that the thermodynamic pressure remains constant throughout the device, as illustrated by Equation \ref{EQ: Pressure_Velocity}. The analysis further simplifies the flow dynamics by disregarding the boundary layer near the extractor's inner wall, leading to a uniform velocity profile across any cross-section perpendicular to the axial direction. Given that the solute concentration in the solvent is negligible, the fluid phase is described as pseudo-homogeneous, with properties identical to the solvent itself. Thus, The mass balance equation encompasses convection, diffusion, and kinetic terms to represent the fluid phase's behaviour accurately.

@@

		The efficiency of the process (the yield) is calculated according to Equation \ref{Model_measurment_1} as presented by \citet{Sovova1994a}. The measurement equation evaluates the solute's mass at the extraction unit's outlet and sums it up. The integral form of the measurement equation (\ref{Model_measurment_1}) can be transformed into the differential form (\ref{Model_measurment_2}) and augmented with the process model.

@@

		\subsubsection{Initial and boundary conditions} 
		It is assumed that the solvent is free of solute at the entrance of the extractor and that all the solid particles have the same initial solute content ${\color{black}c_{s0}}$. As the residence time is much shorter than the sampling time, the initial state estimate for the concentration of the solute in the fluid phase would be not reliable. Considering that it is assumed that the $c_{f0}=0$. Moreover, it is considered that the extractor is isothermal. %and described by ${\color{black}h_0}$. 
		Therefore, the initial and boundary conditions employed in the simulation are:

@@

			{\footnotesize
				\begin{align*}
					&{\color{black}c_f}(t = 0, z) = 0 && c_s(t = 0, z) = {\color{black}c_{s0}} && {c_f}(t, z=0) = 0 \\
					&\frac{\partial c_f(t,z=L)}{\partial x} = 0 && c_s(t, z=\{0,L\}) = 0 && y(0) = 0
			\end{align*} }

@@

		As presented in Appendix \ref{CH: Gouverning equations}, all the governing can be written in the integral form using the Divergence Theorem. The integral equation states that the change rate of the integral of any quantity over an arbitrary control volume is given by the flux through the boundary of the control volume, with being the outer surface normal through the boundary. That quantity is conserved and neither produced nor consumed inside the control volume. For a derivative to be conservative, it must form a telescoping series. In other words, after the addition of all terms coming from the discretization over a grid, only the boundary terms should remain, and the artificial interior points should cancel out. Discretization is applied to the conservative form of the process model to ensure mass conservation.

### 2024-03-19 SFE_article_Parameter_Estimation_short - Chamomile/Sections/introduction_imp.tex
19.03

	This study investigates the extraction of essential oil from chamomile flowers (Matricaria chamomilla L.) via supercritical fluid extraction techniques and modelling of this process. Chamomile is a medicinal herb widely cultivated in southern and eastern Europe—such as Germany, Hungary, France, and Russia. It can be found outside of Europe in Brazil as discussed by \citet{Singh2011}. This plant is distinguished by its hollow, bright gold cones, housing disc or tubular florets and surrounded by about fifteen white ray or ligulate florets. Chamomile has been used for its medicinal benefits, serving as an anti-inflammatory, antioxidant, mild astringent, and healing remedy. Chamomile's aqueous extract is widely used as a gentle sedative to calm nerves and mitigate anxiety, hysteria, nightmares, insomnia, and other sleep-related conditions, according to \citet{Srivastava2009}. \citet{Orav2010} reported that oil yields from dried chamomile samples ranged from 0.7 to 6.7 mL/kg. Notably, the highest yields of essential oil, between 6.1 and 6.7 mL/kg, were derived from chamomile sourced from Latvia and Ukraine, while chamomile from Armenia exhibited a lower oil content of 0.7 mL/kg.

@@

	Evaluating the economic viability of the process is essential when choosing the suitable technology for essential oil extraction. Traditional methods, such as distillation and organic solvent extraction, are commonly employed but come with drawbacks. Distillation, for example, involves high temperatures that can lead to the thermal degradation of heat-sensitive compounds. This limitation has led to the increased popularity of alternative techniques like supercritical fluid extraction. Supercritical carbon dioxide is particularly appealing due to its distinctive properties: it's inflammable, non-toxic, and is non-corrosive. Moreover, its relatively low critical point, compared to other fluids, positions it as an advantageous alternative to conventional extraction methods. Supercritical fluids are capable of exhibiting both gas- and liquid-like properties, allowing for adjustable dissolving power through changes in operating conditions.

	The literature offers a variety of mathematical models aimed at detailing the extraction of valuable compounds from a fixed biomass bed. Selecting a fitting model necessitates a deep understanding of the physical processes at play within the operational unit, as each model is built on specific assumptions and outlines distinct mass transfer mechanisms and equilibrium dynamics.

@@

	This work builds upon the linear kinetic model suggested by \citet{Reverchon1996}, deriving fundamental governing equations to develop a comprehensive model for the chamomile oil extraction process. This model aims for control-oriented simplicity, assuming a semi-continuous operation within a cylindrical vessel. The process involves supercritical solvent being pumped through a fixed bed of finely chopped biomass to extract the solute, followed by separation of the solvent and solute in a flush drum to collect the extract. Parameters such as the feed flow rate ($F_{in}$) and inlet temperature ($T_{in}$) are adjustable and measurable, as is the vessel pressure ($P$), whereas the outlet temperature ($T_{out}$) can only be monitored. A simplified flow diagram is presented in Figure \ref{fig: SFE_drawing}, illustrating the process setup.

@@

	This study focuses on creating a process model for the extraction of natural substances from solid materials using supercritical fluids, with a particular emphasis on supercritical $CO_2$. The approach involves estimating the solvent properties through thermodynamic relationships and determining the extraction kinetic parameters via a series of experiments conducted under a variety of conditions. The maximum likelihood estimator method is employed to address the parameter estimation challenge, with the derived parameters subsequently used to establish correlations. These correlations are instrumental in extending the applicability of the process model across different temperatures (30 to 40$^\circ C$) and pressures (100 to 200 bar).

>>>>

	This study investigates the extraction of essential oil from chamomile flowers (Matricaria chamomilla L.) via supercritical fluid extraction techniques and the modelling of this process. Chamomile is a medicinal herb widely cultivated in southern and eastern Europe—such as Germany, Hungary, France, and Russia. It can be found outside of Europe in Brazil as discussed by \citet{Singh2011}. This plant is distinguished by its hollow, bright gold cones, housing disc or tubular florets and surrounded by about fifteen white ray or ligulate florets. Chamomile has been used for its medicinal benefits, serving as an anti-inflammatory, antioxidant, mild astringent, and healing remedy. Chamomile's aqueous extract is widely used as a gentle sedative to calm nerves and mitigate anxiety, hysteria, nightmares, insomnia, and other sleep-related conditions, according to \citet{Srivastava2009}. \citet{Orav2010} reported that oil yields from dried chamomile samples ranged from 0.7 to 6.7 mL/kg. Notably, the highest yields of essential oil, between 6.1 and 6.7 mL/kg, were derived from chamomile sourced from Latvia and Ukraine, while chamomile from Armenia exhibited a lower oil content of 0.7 mL/kg.

@@

	Evaluating the economic viability of the process is essential when choosing the suitable technology for essential oil extraction. Traditional methods, such as distillation and organic solvent extraction, are commonly employed but come with drawbacks. Distillation, for example, involves high temperatures that can lead to the thermal degradation of heat-sensitive compounds. This limitation has led to the increased popularity of alternative techniques like supercritical fluid extraction. Supercritical carbon dioxide is particularly appealing due to its distinctive properties: it is inflammable, non-toxic, and is non-corrosive. Moreover, compared to other fluids, its relatively low critical point positions it as an advantageous alternative to conventional extraction methods. Supercritical fluids are capable of exhibiting both gas- and liquid-like properties, allowing for adjustable dissolving power through changes in operating conditions.

	The literature offers various mathematical models to detail the extraction of valuable compounds from a fixed biomass bed. Selecting a fitting model necessitates a deep understanding of the physical processes at play within the operational unit, as each model is built on specific assumptions and outlines distinct mass transfer mechanisms and equilibrium dynamics.

@@

	This work builds upon the linear kinetic model suggested by \citet{Reverchon1996}, deriving fundamental governing equations to develop a comprehensive model for the chamomile oil extraction process. This model aims for control-oriented simplicity, assuming a semi-continuous operation within a cylindrical vessel. The process involves supercritical solvent being pumped through a fixed bed of finely chopped biomass to extract the solute, followed by separation of the solvent and solute in a flush drum to collect the extract. Parameters such as the pressure ($P$), feed flow rate ($F_{in}$) and inlet temperature ($T_{in}$) are adjustable and measurable, while the outlet temperature ($T_{out}$) and the amount of product at the outlet can only be monitored. Figure \ref{fig: SFE_drawing} presents a simplified flow diagram illustrating the process setup.

@@

	This study focuses on creating a process model for the extraction of natural substances from solid materials using supercritical fluids, with a particular emphasis on supercritical $CO_2$. The approach involves estimating the solvent properties through thermodynamic relationships and determining the extraction kinetic parameters via a series of experiments conducted under a variety of conditions. The maximum likelihood estimator method is employed to address the parameter estimation challenge, with the derived parameters subsequently used to establish correlations. These correlations are instrumental in extending the applicability of the process model across different temperatures (30 to 40$^\circ C$), pressures (100 to 200 bar) and flow rates (3.33 to 6.67 $\times 10^{-5}$ kg/s).

### 2024-03-19 SFE_article_Parameter_Estimation_short - Chamomile/Short_Supercritical_fluid_extraction_of_essential_oil_from_chamomile.tex
19.03

	The set of quasi-one-dimensional compressible Navier-Stokes equations in Cartesian coordinates are encapsulated by Equations \ref{EQ: CompressibleEuler_1} through \ref{EQ: CompressibleEuler_3}. The formulation of these equations is elaborated upon in Appendix \ref{CH: Gouverning equations}, providing a mathematical foundation for analyzing flow dynamics under the assumed conditions.

{\footnotesize
	\begin{align}
		\label{EQ: CompressibleEuler_1}
		\cfrac{\partial \left( {\color{black}\rho_f} {\color{black}A_f}(z) \right) }{\partial t} + \cfrac{\partial \left( {\color{black}\rho_f} {\color{black}A_f}(z) v \right)}{\partial z} &= 0 \\
		\cfrac{\partial \left( {\color{black}\rho_f} v {\color{black}A_f}(z) \right) }{\partial t} + \cfrac{\partial \left( {\color{black}\rho_f} {\color{black}A_f}(z) v^2 \right)}{\partial z} &= -{\color{black}A_f}(z) \cfrac{\partial {\color{black}P}}{\partial z} \label{EQ: CompressibleEuler_2} \\
		\cfrac{\partial \left( {\color{black}\rho_f} {\color{black}e} {\color{black}A_f}(z) \right) }{\partial t} + \cfrac{\partial \left( {\color{black}\rho_f} {\color{black}A_f}(z) v {\color{black}e}\right)}{\partial z} &= -{\color{black}P}\cfrac{\left( {\color{black}A_f}(z) v \right)}{\partial z} + \cfrac{\partial}{\partial z} \left( \cfrac{\partial {\color{black}T}}{\partial z} \right)   
		\label{EQ: CompressibleEuler_3}
	\end{align}  
}

@@

Suppose the flow is presumed to be isentropic, $d{\color{black}P}/d{\color{black}\rho_f} = c^2$, so $v^2=c^2$, where $c$ is the speed of sound. This can be interpreted as a small pressure wave propagating with the speed of sound relative to the flow. Moreover, if the flow velocity is relatively low, all pressure changes are hydrodynamic (due to velocity motion) rather than thermodynamic which leads to $\partial {\color{black}\rho_f} / \partial {\color{black}P} \approx 0$. In other words, the small changes in pressure due to flow velocity changes do not change the density.

The low Mach number condition leads to the incompressible condition: $\nabla \cdot u =0$, which is valid for constant density (strict incompressible) or varying density flow. The restraint allows for the removal of acoustic waves, but also allows for large perturbations in density and/or temperature. The assumption is that the flow remains within a Mach number limit (normally less than 0.3) for any solution using such a constraint to be valid. In 1-D case the incompressibility condition becomes $\frac{du}{dz} = 0$, so the fluid velocity is constant.

@@

\clearpage \appendix \label{appendix}
\section{Appendix} 
\subsection{Thermodynamic}
\subfile{Sections/Qubic_EOS}

@@

>>>>

	The set of quasi-one-dimensional compressible Navier-Stokes equations in Cartesian coordinates are described by Equations \ref{EQ: CompressibleEuler_1} through \ref{EQ: CompressibleEuler_3}. The formulation of these equations is elaborated upon in Appendix \ref{CH: Gouverning equations}, providing a mathematical foundation for analyzing flow dynamics under the assumed conditions.

{\footnotesize
	\begin{align}
		\label{EQ: CompressibleEuler_1}
		\cfrac{\partial \left( {\color{black}\rho_f} {\color{black}A_f}(z) \right) }{\partial t} + \cfrac{\partial \left( {\color{black}\rho_f} {\color{black}A_f}(z) v \right)}{\partial z} &= 0 \\
		\cfrac{\partial \left( {\color{black}\rho_f} v {\color{black}A_f}(z) \right) }{\partial t} + \cfrac{\partial \left( {\color{black}\rho_f} {\color{black}A_f}(z) v^2 \right)}{\partial z} &= -{\color{black}A_f}(z) \cfrac{\partial {\color{black}P}}{\partial z} \label{EQ: CompressibleEuler_2} \\
		\cfrac{\partial \left( {\color{black}\rho_f} {\color{black}e} {\color{black}A_f}(z) \right) }{\partial t} + \cfrac{\partial \left( {\color{black}\rho_f} {\color{black}A_f}(z) v {\color{black}e}\right)}{\partial z} &= -{\color{black}P}\cfrac{\left( {\color{black}A_f}(z) v \right)}{\partial z} + \cfrac{\partial}{\partial z} \left( k \cfrac{\partial {\color{black}T}}{\partial z} \right)   
		\label{EQ: CompressibleEuler_3}
	\end{align}  
}

@@

Suppose the flow is presumed to be isentropic, $d{\color{black}P}/d{\color{black}\rho_f} = c^2$, so $v^2=c^2$, where $c$ is the speed of sound. This can be interpreted as a small pressure wave propagating with the speed of sound relative to the flow. If the flow velocity is relatively low, all pressure changes are hydrodynamic (due to velocity motion) rather than thermodynamic, which leads to $\partial {\color{black}\rho_f} / \partial {\color{black}P} \approx 0$. The small changes in pressure due to flow velocity changes do not change the density.

The low Mach number condition leads to the incompressible condition: $\nabla \cdot u =0$, which is valid for constant density (strict incompressible) or varying density flow. The restraint allows for the removal of acoustic waves, but also allows for large perturbations in density and/or temperature. The assumption is that the flow remains within a Mach number limit (usually less than 0.3) for any solution using such a constraint to be valid. In the 1-D case, the incompressibility condition becomes $\frac{du}{dz} = 0$, so the fluid velocity is constant.

@@

\clearpage \appendix \label{appendix}
\section{Appendix}

@@

\subsection{Thermodynamic}
\subfile{Sections/Qubic_EOS} \label{CH: EOS}

### 2024-03-19 SFE_article_Sensitivity_Analysis - Chamomile/Article_Sensitivity_Analsysis-Chamomile.tex
19.03

% ===================================================
% ABSTRACT
% ===================================================
\begin{abstract}
This study aimed to investigate the supercritical extraction process of caraway oil from caraway seeds. The extraction was performed in a partially filled extractor with a fixed bed operated under multiple operating conditions. A distributed-parameter model describes the fluid-solid extraction process with $CO_2$ as a solvent. The concept of quasi-one-dimensional flow is applied to reduce the number of spatial dimensions. The flow is assumed to be uniform across any cross-section, although the area available for the fluid phase can vary along the extractor. The local sensitivity analysis investigates the influence of infinitely small changes in the inlet temperature, pressure, and flow rate on the extraction yield.

@@

The study is structured as follows: Chapter \ref{CH: Thermodynamic} provides a general discussion on supercritical fluids to familiarize the reader with their properties. Chapter \ref{CH:Governing_equations_chapter} introduces the general balance equations. The balance equations are combined with the extraction kinetic equation to develop the process model in Chapter \ref{CH: Extraction_model}. The derivative-based local sensitivity analysis is presented in Chapter \ref{CH: Sensitivity_Analysis} and is then combined with the process model. Finally, the sensitivity plots are discussed in Chapters \ref{CH: Results} and \ref{CH: Conclusion}.

>>>>

% ===================================================
% ABSTRACT
% ===================================================
\begin{abstract}
This study aimed to investigate the supercritical extraction process of caraway oil from chamomile flowers. The distributed-parameter model describes the fluid-solid extraction process. The concept of quasi-one-dimensional flow is applied to reduce the number of spatial dimensions. The flow is assumed to be uniform across any cross-section, although the area available for the fluid phase can vary along the extractor. The physical properties of the solvent are estimated from the Peng-Robinson equation of state. A set of laboratory experiments was performed under multiple constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \times 10^{-5}$ kg/s. Sensitivity analyses play a crucial role in assessing the robustness of the findings or conclusions based on mathematical model. The local sensitivity analysis investigates the influence of infinitely small changes in the inlet temperature, pressure, and flow rate on the extraction yield.

@@

%The study is structured as follows: Chapter \ref{CH: Thermodynamic} provides a general discussion on supercritical fluids to familiarize the reader with their properties. Chapter \ref{CH:Governing_equations_chapter} introduces the general balance equations. The balance equations are combined with the extraction kinetic equation to develop the process model in Chapter \ref{CH: Extraction_model}. The derivative-based local sensitivity analysis is presented in Chapter \ref{CH: Sensitivity_Analysis} and is then combined with the process model. Finally, the sensitivity plots are discussed in Chapters \ref{CH: Results} and \ref{CH: Conclusion}.

### 2024-03-19 SFE_article_Sensitivity_Analysis - Chamomile/Sections/Literature_Review.tex
19.03

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	This study aims to analyze the influence of changes in operating conditions on the supercritical extraction process described in {\color{red}article 1}. The emphasis is put on the effect of the mass flow rate, pressure, and the inlet temperature. The relation between input and output is obtained by applying a sensitivity analysis. Sensitivity analysis examines the impact of varying inputs or model parameters on the uncertainty of a mathematical model or system's output. The aim is to understand and to allocat the source of uncertainty in the output to the corresponding inputs or parameters. There are many sensitivity analysis methods, which include but are not limited to those listed below:

>>>>

\documentclass[../Article_Sensitivity_Analsysis.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	This study aims to analyze the influence of changes in operating conditions on the supercritical extraction process described in {\color{red}article 1}. The emphasis is put on the effect of the mass flow rate, pressure, and the inlet temperature. The relation between input and output is obtained by applying a sensitivity analysis. Sensitivity analysis examines the impact of varying inputs or model parameters on the system's output. The aim is to understand and to allocate the source of uncertainty in the output to the corresponding inputs or parameters. There are many sensitivity analysis methods, which include but are not limited to those listed below:
